\propertitle

### 2019-12-21 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-21T23:54:35+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

% The conclusions about \enquote{cooperativity} or \enquote{interaction} that
% we reach by applying the maximum-entropy method to the larger population,
% as proposed here, are therefore different from those applying it at the
% sample level -- and also visually clearer. The plot in 
% \fig~\ref{fig:plots_2_4mom_a}, showing the two clearly different
% distributions constrained by two and four moments, should be compared with
% the plot for the distributions obtained at the sample level under the same
% constraints, shown in \fig~\ref{fig:comparisons_marginals} as
% \textcolor{myred}{red circles} and \textcolor{myblue}{blue squares}. The
% measured frequencies (black triangles) are also shown. It is necessary to
% use a logarithmic scale to see the differences, which appear mainly in the
% tail.
\begin{figure}[!p]
\centering
% \includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
% \\[3em]%
\includegraphics[width=0.95\linewidth]{_scripts/trunct2_comparison_marginals.pdf}%
\caption{Maximum-entropy distributions constructed at the sample level
  ($N=n$), based on the first two, four, and five moments; and sample
  marginal of the distribution constructed with five moments for a larger
  population with $N=10\,000$ (dotted yellow in
  \subcaptionref{fig:plots_2_4mom_a}). The distributions at the sample
  level are all very similar, only distinguishable on a logarithmic scale.
  The five-moment distribution constructed at the larger-population level
  fits the frequency data better than the one at the sample level.}
\label{fig:comparisons_marginals}
\end{figure}
% comparison_ME_sample_full_levels.nb

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-22T00:23:26+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

% The conclusions about \enquote{cooperativity} or \enquote{interaction} that
% we reach by applying the maximum-entropy method to the larger population,
% as proposed here, are therefore different from those applying it at the
% sample level -- and also visually clearer. The plot in 
% \fig~\ref{fig:plots_2_4mom_a}, showing the two clearly different
% distributions constrained by two and four moments, should be compared with
% the plot for the distributions obtained at the sample level under the same
% constraints, shown in \fig~\ref{fig:comparisons_marginals} as
% \textcolor{myred}{red circles} and \textcolor{myblue}{blue squares}. The
% measured frequencies (black triangles) are also shown. It is necessary to
% use a logarithmic scale to see the differences, which appear mainly in the
% tail.
\begin{figure}[!p]
\centering
% \includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
% \\[3em]%
\includegraphics[width=0.92\linewidth]{_scripts/trunct2_comparison_marginals.pdf}%
\caption{Maximum-entropy distributions constructed at the sample level,
  using the first two, four, and five moments; and sample marginal of the
  distribution constructed with five moments for a larger population with
  $N=10\,000$ (dotted yellow in \ref{fig:plots_2_4mom_a}). The
  distributions are multiplied by $T$, obtaining absolute frequencies; note
  that activities with frequency lower than 1 cannot be observed in $T$
  bins. The distributions at the sample level are only distinguishable on a
  logarithmic scale. The five-moment distribution constructed at the
  larger-population level fits the frequency data better than the one at
  the sample level.}
\label{fig:comparisons_marginals}
\end{figure}
% comparison_ME_sample_full_levels.nb
